Arrows for Parallel Computations

### 2017-07-25 paper/content/benchmarks.tex
minor fix in benchmarks.tex (clarified that we have multiple Gentleman Multiplications at once) pdf for olegs changes

\begin{table}
\caption{The benchmarks we use in this paper.}
\label{tab:benches}
\centering
%% something was wrong with separators in table
\renewcommand{\tabcolsep}{1em}
\begin{tabular}{lccll}
\toprule
Name & Area & Type & Origin & Citation \\
\midrule
\rmtest & Mathematics & |parMap+reduce| & Eden & \citet{Lobachev2012}\\
Jacobi sum test & Mathematics & |workpool+reduce| & Eden & \citet{Lobachev2012}\\
Gentleman & Mathematics & |torus| & Eden & \citet{Loogen2012}\\
Sudoku & Puzzle & |parMap| & |Par| Monad & \citet{par-monad}\\
\bottomrule
\end{tabular}
\end{table}

@@

``Gentleman'' is a standard Eden test program, developed
for their |torus| skeleton. It implements a parallel matrix
multiplication \citep{Gentleman1978}. We ported its latest Eden
version \citep{Loogen2012} to PArrows.

>>>>

\begin{table}
\caption{The benchmarks we use in this paper.}
\label{tab:benches}
\centering
%% something was wrong with separators in table
\renewcommand{\tabcolsep}{1em}
\begin{tabular}{lccll}
\toprule
Name & Area & Type & Origin & Citation \\
\midrule
\rmtest & Mathematics & |parMap+reduce| & Eden & \citet{Lobachev2012}\\
Jacobi sum test & Mathematics & |workpool+reduce| & Eden & \citet{Lobachev2012}\\
Gentleman & Mathematics & |torus+parMap| & Eden & \citet{Loogen2012}\\
Sudoku & Puzzle & |parMap| & |Par| Monad & \citet{par-monad}\\
\bottomrule
\end{tabular}
\end{table}

@@

``Gentleman'' is a standard Eden test program, developed
for their |torus| skeleton. It implements a parallel matrix
multiplication \citep{Gentleman1978}. We ported its latest Eden
version \citep{Loogen2012} to PArrows and changed it so that it runs multiple |torus| computations in parallel with |parMap|.
